The reference model approach in feature selection problems \vspace{.1in}

### 2019-06-28 paper/ref_approach.tex
updated paper: projpred description, bodyfat steplm analysis, explanation of fdr and EBmed, minor edits

In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection, which is a special case of model reduction. The necessity of carrying out the selection arises from different problematics. Sometimes the leading objective of the analysis is to predict future observations, thus the main focus in building the model is on the predictive performance. Yet a high dimensional parameter space often leads to dangers as overfitting or other technical problems, as expensive costs to collect all the features or computational and memory burdens (e.g. when we are operating on limited resources), and thus a sparser representation of the model would be preferred. In addition to that, simpler models bring also advantages in terms of interpretability. Some other times, variable selection can be also seen as an inferential tool: the interest is on knowing which variables are meaningful, or relevant, in relation to the target variable of interest. This typically happens in a \textit{small n large p} scenario, as in many microarray data analysis in medicine or biology. A very large number of genes is usually analysed in two groups of individuals labeled as \textit{positive} or \textit{negative} to some disease; the goal is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{efron2012large}.

Either the target of the selection is the minimal subset of feature with good enough predictive ability, or the whole subset of relevant variables, the selection process is going to be based on assumptions regarding the ``true'' data generation mechanism. Making assumptions means making models, thus we identify two families of feature selection, or more in general model reduction, approaches depending on how the data generation mechanism is modelled: the data based and the reference model based ones. The former includes all those methods that use the observed empirical distribution as model approximation of the data generation mechanism, as for example happens in the Lasso selection \cite{tibshirani1996regression} or in the stepwise backward/forward regression, where the selected submodels balance sparsity with predictive ability on the observed data. The reference model based methods use instead the predictive distribution of a full-encompassing model, i.e. the reference model, as an approximation of the data generation mechanism. Such an idea is widely present in the literature with different names; for example, \cite{harrell2015regression} refers to the reference model as a full model that can be thought as the ``gold standard'' and shows some examples of how it can be used to look for a sparser approximation. He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximates the best model and the inheritance of the shrinkage when it is applied to the full model. \cite{faraggi2001understanding} deal with the necessity of identifying interpretable risk groups in the context of survival data using neural networks, which typically perform very well in terms of prediction, but whose covariates are difficult to be understood in terms of relevance. \cite{faraggi2001understanding} propose to combine the benefits of the neural networks, which become what we call reference models, with the interpretability of regression trees, in order to provide a framework to make inferences about risk groups. \cite{paul2008preconditioning}, using the term preconditioning, explore approximating models fitting Lasso or stepwise regression against consistent estimates $\hat{y}$ of a reference model instead of the observed response quantities $y$. 

@@

A good predictive model is able to clean part of the noise present in the data. The noise is the main source of the instability and tends to obscure the relevance of the covariates in relation to the target variable of interest. Indeed, let us consider the following explanatory example taken from \cite{paper:projpred}. The data generation mechanism for each statistical unit is the following:
\
\begin{alignat}{2} \label{eq:simulated_data}
     &f\sim N(0,1) && \nonumber \\ 
     Y|&f\sim N(f,1) && \\
     X_{j}|&f \overset{iid}{\sim} N(\sqrt{\rho}f,1-\rho) \quad &&j=1,..,k \nonumber \\
     X_{j}|&f \overset{iid}{\sim} N(0,1) &&j=k+1,..,p \nonumber
\end{alignat}
$f$ is the latent variable of interest of which $Y$ is a noisy observation. The first $k$ covariates are significantly related to the target variable $Y$ and correlated among themselves. Precisely, $\rho$ is the correlation among any pair of the first $k$ covariates, whereas $\sqrt{\rho}$ and $\sqrt{\rho}/2$ are the level of correlation between any significant covariate and respectively $f$ and $Y$. If we had an infinite amount of observations, the sample correlation would be equal to the true correlation, though, even in this ideal asymptotic regime, the correlation computed would be still a biased indicator of the true relevance of each variable with respect to the latent variable of interest due to the intrinsic noisy nature of $Y$. When using a reference model, we are trying to model $f$ through the covariates $\{X_{j}\}_{j=1}^{p}$ taking in account that what we observe (i.e. $Y$) is corrupted by noise. Thus, if our model is good, we are able to describe $f$ better than the simply observed variable $Y$ and to use such information to assess the relevance of the features. Indeed, Figure \ref{fig:correlation} shows the scatter plot of the absolute value of the sample correlation of each feature with the point prediction by a reference model, in this case see model \eqref{eq:ref_mod}, against the absolute value of the sample correlation of each feature with the noisy observations $\{y\}_{i=1}^{n}$. Looking at the marginal distribution, we observe that using a reference model the two group of features, i.e. relevant and non-relevant, have a minor overlap, and thus can be better distinguished, with respect to when the correlation is computed using directly the observed data. We can think about the correlation as a general indicator of the relevance of a feature.

@@

Relying on the idea of the reference model as a noise-filter, a simple, but effective, reference model approach which can be used on top of any feature selection procedure consists in substituting the target observations with a point prediction of the reference model, e.g. posterior predictive mean. Afterwards, any method for feature selection can be used. In Section \ref{comparison} we compare some well-known methods from the literature using both such reference model approach and the original data, observing at the end of the selection higher stability and quality of the selection thanks to the reference model.

@@

As a motivational example to the study of the consequences of the use of a reference model in feature selection problems, we show its application in the form of the projection predictive approach, which uses the reference model to project the posterior samples in the submodels. The R-package \textit{projpred} (available at \url{https://CRAN.R-project.org/package=projpred}) implements the projection in case of submodels in the family of the generalised linear models and, additionally, it provides a framework to choose the optimal submodel size through a predictive utility comparison between the submodels and the reference model. 
\\
We now summarise the workflow of the projection predictive approach in the particular case of the draw-by-draw projection \cite[original formulation by][]{paper:original_proj}, following \cite{paper:projpred}. Assume to have $n$ statistical units with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed covariates, the main step are the followings:
\begin{enumerate}
\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of S posterior samples of the vector parameter of the model.
\item Rank the covariates using a heuristics and consider as candidate submodels the nested ones, starting to include the best ranked feature. The submodel are naturally identify by their model size.
\item For each submodel, project the reference model samples as follows:
\begin{equation}\label{eq:draw_by_draw}
\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL}\;[p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\,||\,p(\tilde{y}_{i}|\boldsymbol{\theta}^{s})] \quad s=1,..,S
\end{equation}
where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the model distribution of the reference model with parameters fixed at the sample value $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariates related to the statistical unit (identified by the subscript $i$ in the variable $\tilde{y}_{i}$), whereas $p(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ the same but for the submodel.
\item For each submodel (size), test the predictive performance.
\item Choose the smallest submodel (size) that is sufficiently close to the reference model prediction utility score.
\end{enumerate}

@@

\cite{paper:bodyfat} report the results using the stepwise backward elimination with a significance level of 0.157 with AIC selection, fixing abdomen and height to be always included in the model. We implement the selection via projection: the reference model includes all the covariates using as a prior the regularised horseshoe, submodels are explored using a forward search and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}. In order to automatise the procedure, we select the submodel size as the smallest one which has an elpd score higher than the reference model score with probability 0.05. Figure \ref{fig:inclusion_frequencies} shows the bootstrap inclusions frequencies combining the results from \cite{paper:bodyfat} for the stepwise backward elimination and our experiments for the projection. The projection predictive approach has only two variables with inclusion frequencies above 50\% (abdomen is the only included always), the third most included is `wrist' at 49.5\% and the fourth is `height' at 27.8, while the stepwise regression has seven features above 50\%, of which abdomen and height are fixed. Such a lower stability of the stepwise regression can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}. The first five selected models have a cumulative frequency of almost 70\% with projpred, whereas with the stepwise regression only of 11.8\%. In addition to that we note that the size of the selected model is much smaller when using projpred.

@@

\hypertarget{complete-selection}{%
\subsubsection{Complete selection analysis}\label{complete-selection}}
As complete selection procedures we consider the control of the local false discovery rate \citep{paper:efron, efron2012large}, the empirical Bayes median \citep{johnstone2004needles} and the selection by posterior credible intervals. 
\\
The control of the local false discovery rate is applied through the R-package \textit{locfdr}. It consists in testing the z-values $\{z_{j}\}_{j=1}^{p}$ to belong to the theoretical null distribution $f_{0}$ (the null hypothesis, meaning no relevance) against the alternative hypothesis distribution $f_{1}$. In our case $f_{0}$ correspond to the standard normal distribution (see expression \eqref{eq:normal_means_problem2}). The quantity of interest is the local false discovery rate (loc.fdr) defined as:
\
\begin{equation}
loc.fdr(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)}
\end{equation}
where $\pi_{0}$ is the prior probability of the null hypothesis and $f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal distribution of the z-values. The latter is estimated using splines with 7 degrees of freedom and we select features with local false discovery rate under the value 0.2. Such a value is commonly suggested only because it corresponds to a Bayes factor large than 36 (assuming $\pi_{0}\geq0.9$), other values can be considered and in our experience do not affect the results of the comparison. We use the default setting to estimate $\pi_{0}$ from the data provided by the package.
\\
The empirical Bayes median procedure is given by the R-package \textit{EbayesThresh} and consists in fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution. We use, as suggested, a Laplace distribution resulting in a thresholding property, i.e. there exists a threshold value such that all the data under that threshold have posterior median equal to zero. Therefore the selection is done including those parameters whose posterior median is different from zero. The hyperparameter of the Laplace distribution and the mixing weight of the prior are estimated by marginal maximum likelihood. 
\\
The selection by posterior credible intervals is done using the regularised horseshoe prior and selecting those features who do not include zero in the interval between the 0.05 and the 0.95 quantiles.

@@

We conclude our experiments using the real world dataset body fat, already described in the comparison between the projection predictive approach and the stepwise regression in Section \ref{projection}. Consistently with the previous comparisons, we design the variable selection by normal means problem. We add to the original data noisy uncorrelated covariates up to a total of 1000 features. These covariates are normally distributed and scaled as the original ones. We compute correlations between each variable and the target variable, that is the amount of fat, and transform them by Fisher transformation. The original assumption, in order that \eqref{eq:fisher_transformation} holds, is that the variables are jointly normally distributed. In our experience the normal approximation is still reasonable, but after rescaling by $\sqrt{n-3}$ we do not fix the variance to be one, but we estimate it from the data. The methods we compare are those used in Section \ref{complete-selection}: the control of the local false discovery rate (loc.fdr), the empirical Bayes median (EB.med) and the selection by posterior credible intervals at level 0.9 (ci.90). The maximum likelihood estimator is used to estimate the variance of the null hypothesis in the local false discovery rate \cite[see][Chap. 6]{efron2012large}, whereas the median absolute deviation from zero for the empirical Bayes median method. The selection via posterior credible intervals is done using a regularised horseshoe prior on the parameters for the means, while a standard log-normal  prior for the variance. In order to vary the difficulty of the selection, we bootstrap subsamples of different sizes, going from $n=50$ up to $n=251$. Each time results are averaged over 100 bootstrap subsamples.

@@

Figure \ref{fig:bodyfat_sensitivity_vs_fdr} shows the sensitivity against the false discovery rate. Since we do not have a ground truth regarding the original covariates of the data, we believe it is reasonable to consider all of them relevant, at least at some degree. We thus consider as non-relevant all the artificially added ones. In almost all the bootstrapped subsamples, the reference model improves both in terms of sensitivity and false discovery rate. When $n=50$, we observe a worsening in terms of false discovery rate, yet in a lower amount compared to the gain in sensitivity.  We observe again that the benefits are more evident as the selection is more challenging (i.e. less number of observations).
\\
Figure \ref{fig:bodyfat_stability} shows the stability results, still using the measure provided by \cite{paper:stability}. The benefits of the reference model are here marginal: small improvements can be observed, but overall not very notable.

>>>>

In statistical applications, one of the main steps of the modelling workflow is covariate or feature selection, which is a special case of model reduction. The necessity of carrying out the selection arises from different problematics. Sometimes the leading objective of the analysis is to predict future observations, thus the main focus in building the model is on the predictive performance. Yet a high dimensional parameter space often leads to dangers as overfitting or other technical problems, as expensive costs to collect all the features for future observations or computational and memory burdens (e.g. when we are operating on limited resources), and thus a sparser representation of the model would be preferred. In addition to that, simpler models bring also advantages in terms of interpretability. Some other times, variable selection can be also seen as an inferential tool: the interest is on knowing which variables are meaningful, or relevant, in relation to the target variable of interest. This typically happens in a \textit{small n large p} scenario, as in many microarray data analysis in medicine or biology. A very large number of genes is usually analysed in two groups of individuals labeled as \textit{positive} or \textit{negative} to some disease; the goal is to spot the subset of explanatory genes in order to perform further experiments \cite[see examples in][]{efron2012large}.

Either the target of the selection is the minimal subset of feature with good enough predictive ability, or the whole subset of relevant variables, the selection process is going to be based on assumptions regarding the ``true'' data generation mechanism. Making assumptions means making models, thus we identify two families of feature selection, or more in general model reduction, approaches depending on how the data generation mechanism is modelled: the data based and the reference model based ones. The former includes all those methods that use the observed empirical distribution as model approximation of the data generation mechanism, as for example happens in the Lasso selection \cite{tibshirani1996regression} or in the stepwise backward/forward regression, where the selected submodels balance sparsity with predictive ability on the observed data. The reference model based methods use instead the predictive distribution of a full-encompassing model, i.e. the reference model, as an approximation of the data generation mechanism. Such an idea is widely present in the literature with different names; for example, \cite{harrell2015regression} refers to the reference model as a full model that can be thought as the ``gold standard'' and shows some examples of how it can be used to seek a sparser approximation. He highlights some of the benefits as the possibility to calculate the accuracy with which the submodel approximates the best model and the inheritance of the shrinkage when it is applied to the full model. \cite{faraggi2001understanding} deal with the necessity of identifying interpretable risk groups in the context of survival data using neural networks, which typically perform very well in terms of prediction, but whose covariates are difficult to be understood in terms of relevance. \cite{faraggi2001understanding} propose to combine the benefits of the neural networks, which become what we call reference models, with the interpretability of regression trees, in order to provide a framework to make inferences about risk groups. \cite{paul2008preconditioning}, using the term preconditioning, explore approximating models fitting Lasso or stepwise regression against consistent estimates $\hat{y}$ of a reference model instead of the observed response quantities $y$. 

@@

A good predictive model is able to clean part of the noise present in the data. The noise is the main source of the instability and tends to obscure the relevance of the covariates in relation to the target variable of interest. Indeed, let us consider the following explanatory example taken from \cite{paper:projpred}. The data generation mechanism for each statistical unit is the following:
\
\begin{alignat}{2} \label{eq:simulated_data}
     &f\sim N(0,1) && \nonumber \\ 
     Y|&f\sim N(f,1) && \\
     X_{j}|&f \overset{iid}{\sim} N(\sqrt{\rho}f,1-\rho) \quad &&j=1,..,k \nonumber \\
     X_{j}|&f \overset{iid}{\sim} N(0,1) &&j=k+1,..,p \nonumber
\end{alignat}
$f$ is the latent variable of interest of which $Y$ is a noisy observation. The first $k$ covariates are significantly related to the target variable $Y$ and correlated among themselves. Precisely, $\rho$ is the correlation among any pair of the first $k$ covariates, whereas $\sqrt{\rho}$ and $\sqrt{\rho}/2$ are the level of correlation between any significant covariate and respectively $f$ and $Y$. If we had an infinite amount of observations, the sample correlation would be equal to the true correlation, though, even in this ideal asymptotic regime, the correlation computed would be still a biased indicator of the true relevance of each variable with respect to the latent variable of interest due to the intrinsic noisy nature of $Y$. When using a reference model, we are trying to model $f$ through the covariates $\{X_{j}\}_{j=1}^{p}$ taking in account that what we observe (i.e. $Y$) is corrupted by noise. Thus, if our model is good, we are able to describe $f$ better than the simply observed variable $Y$ and to use such information to assess the relevance of the features. Indeed, Figure \ref{fig:correlation} shows the scatter plot of the absolute value of the sample correlation of each feature with the point prediction by a reference model, in this case see model \eqref{eq:ref_mod}, against the absolute value of the sample correlation of each feature with the noisy observations $\{y\}_{i=1}^{n}$. Looking at the marginal distribution, we observe that using a reference model the two groups of features, i.e. relevant and non-relevant, have a minor overlap, and thus can be better distinguished, with respect to when the correlation is computed using directly the observed data. We can think about the correlation as a general indicator of the relevance of a feature.

@@

Relying on the idea of the reference model as a noise-filter, a simple reference model approach, which can be used on top of any feature selection procedure, consists in substituting the target observations with a point prediction of the reference model, e.g. posterior predictive mean. Afterwards, any method for feature selection can be used. Note that we do not argue that such reference model approach should be used as a feature selection tool in real applications; there are many other and more sophisticated ones available in the literature. The reason of this simple approach is to have a fair comparison between using a reference model or not with exactly the same selection procedure. Other kinds of comparison, as the one in Section \ref{projection}, work well as motivational examples, but fail in terms of generality, resulting in a not principled comparison since the presence of the reference model is not the only thing differentiating the two procedures. In Section \ref{comparison} we compare some well-known methods from the literature using both such reference model approach and the original data, observing at the end of the selection higher stability and quality of the selection thanks to the reference model.

@@

As a motivational example to the study of the consequences of the use of a reference model in feature selection problems, we show its application in the form of the projection predictive approach, which uses the reference model to project the posterior samples in the submodels. The R-package \textit{projpred} (available at \url{https://CRAN.R-project.org/package=projpred}) implements the projection in case of submodels in the family of the generalised linear models and, additionally, it provides a framework to choose the optimal submodel size through a predictive utility comparison between the submodels and the reference model. 
\\
We now summarise the workflow of the projection predictive approach in the particular case of the draw-by-draw projection \cite[original formulation by][]{paper:original_proj}, following \cite{paper:projpred}. Assume to have $n$ statistical units with target values $\{y_{i}\}_{i=1}^{n}$ and a set of observed covariates, the main steps are the following:
\begin{enumerate}
\item Devise and fit a reference model. Let $\{\boldsymbol{\theta}_{*}^{s}\}_{s=1}^{S}$ be the set of S posterior samples of the vector parameter of the model.
\item Rank the covariates using a heuristics and consider as candidate submodels the nested ones, starting to include the best ranked feature. The submodel are naturally identify by their model size.
\item For each submodel, project the reference model samples as follows:
\begin{equation}\label{eq:draw_by_draw}
\boldsymbol{\theta}_{\perp}^{s} = \underset{\boldsymbol{\theta}\in\Theta}{\text{argmin}} \frac{1}{n}\sum_{i=1}^{n}\text{KL}\;[p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})\,||\,p(\tilde{y}_{i}|\boldsymbol{\theta}^{s})] \quad s=1,..,S
\end{equation}
where $p(\tilde{y}_{i}|\boldsymbol{\theta}_{*}^{s})$ stands for the model distribution of the reference model with parameters fixed at the sample value $\boldsymbol{\theta}_{*}^{s}$ and conditioning on all the covariates related to the statistical unit (identified by the subscript $i$ in the variable $\tilde{y}_{i}$), whereas $p(\tilde{y}_{i}|\boldsymbol{\theta}^{s})$ the same but for the submodel. The projected samples correspond to the submodel parameter distribution.
\item For each submodel (size), test the predictive performance.
\item Choose the smallest submodel (size) that is sufficiently close to the reference model prediction utility score.
\end{enumerate}

@@

\cite{paper:bodyfat} report the results using the stepwise backward elimination with a significance level of 0.157 with AIC selection, fixing abdomen and height to be always included in the model. We implement the selection via projection: the reference model includes all the covariates using as a prior the regularised horseshoe, submodels are explored using a forward search and the predictive utility is the expected log-predictive density (elpd) estimated using PSIS-LOO \citep{paper:psis_loo}. In order to automatise the procedure, we select the submodel size as the smallest one which has an elpd score higher than the reference model score with probability 0.05. Figure \ref{fig:inclusion_frequencies} shows the bootstrap inclusion frequencies combining the results from \cite{paper:bodyfat} for the stepwise backward elimination and our experiments for the projection. The projection predictive approach has only two variables with inclusion frequencies above 50\% (abdomen is the only included always), the third most included is `wrist' at 49.5\% and the fourth is `height' at 27.8\%, while the stepwise regression has seven features above 50\%, of which abdomen and height are fixed. Such a lower stability of the stepwise regression can be observed also in the bootstrap model selection frequencies reported in Table \ref{tab:model_frequencies}. The first five selected models have a cumulative frequency of almost 70\% with projpred, whereas with the stepwise regression only of 11.8\%. In addition to that we note that the size of the selected model is much smaller when using projpred.

@@

\hypertarget{complete-selection}{%
\subsubsection{Complete selection analysis}\label{complete-selection}}
As complete selection procedures we consider the control of the local false discovery rate \citep{paper:efron, efron2012large}, the empirical Bayes median \citep{johnstone2004needles} and the selection by posterior credible intervals. 
\\
The control of the local false discovery rate is applied through the R-package \textit{locfdr}. It consists in testing the z-values $\{z_{j}\}_{j=1}^{p}$ to belong to the theoretical null distribution $f_{0}$ (the null hypothesis, meaning no relevance) against the alternative hypothesis distribution $f_{1}$. In our case $f_{0}$ correspond to the standard normal distribution, see expression \eqref{eq:normal_means_problem2}. The quantity of interest is the local false discovery rate (loc.fdr) defined as:
\
\begin{equation}
loc.fdr(z)=P(H_{0}|z)=\frac{f_{0}(z)\pi_{0}}{f(z)}
\end{equation}
where $\pi_{0}$ is the prior probability of the null hypothesis and $f(z)=\pi_{0}f_{0}(z)+(1-\pi_{0})f_{1}(z)$ is the marginal distribution of the z-values. The latter is estimated using splines with 7 degrees of freedom and we select features with local false discovery rate under the value 0.2. Such a value is commonly suggested only because it corresponds to a Bayes factor large than 36 (assuming $\pi_{0}\geq0.9$), other values can be considered and in our experience do not affect the results of the comparison. We use the default setting to estimate $\pi_{0}$ from the data provided by the package.
\\
The empirical Bayes median procedure is given by the R-package \textit{EbayesThresh} and consists in fitting a Bayesian model with a prior composed by a mixture of a delta in zero and a heavy-tailed distribution. We use, as suggested, a Laplace distribution resulting in a thresholding property, i.e. there exists a threshold value such that all the data under that threshold have posterior median equal to zero. Therefore the selection is done including those parameters whose posterior median is different from zero. The hyperparameter of the Laplace distribution and the mixing weight of the prior are estimated by marginal maximum likelihood. 
\\
The selection by posterior credible intervals is done using the regularised horseshoe prior and selecting those features whose posterior distribution does not include zero in the interval between the 0.05-th and the 0.95-th quantiles.

@@

We conclude our experiments using the real world dataset body fat, already described in the comparison between the projection predictive approach and the stepwise regression in Section \ref{projection}. Consistently with the previous comparisons, we design the variable selection by normal means problem. We add to the original data noisy uncorrelated covariates up to a total of 1000 features. These covariates are normally distributed and scaled as the original ones. We compute correlations between each variable and the target variable, that is the amount of fat, and transform them by Fisher transformation. The original assumption, in order that \eqref{eq:fisher_transformation} holds, is that the variables are jointly normally distributed. In our experience the normal approximation in \eqref{eq:fisher_transformation} is still reasonable, but after rescaling by $\sqrt{n-3}$ we do not fix the variance to be one, instead we estimate it from the data. The methods we compare are those used in Section \ref{complete-selection}: the control of the local false discovery rate (loc.fdr), the empirical Bayes median (EB.med) and the selection by posterior credible intervals at level 0.9 (ci.90). The maximum likelihood estimator is used to estimate the variance of the null hypothesis in the local false discovery rate \cite[see][Chap. 6]{efron2012large}, whereas the median absolute deviation from zero for the empirical Bayes median method. The selection via posterior credible intervals is done using a regularised horseshoe prior on the parameters for the means, while a standard log-normal  prior for the variance. In order to vary the difficulty of the selection, we bootstrap subsamples of different sizes, going from $n=50$ up to $n=251$. Each time results are averaged over 100 bootstrap subsamples.

@@

Figure \ref{fig:bodyfat_sensitivity_vs_fdr} shows the sensitivity against the false discovery rate. Since we do not have a ground truth regarding the original covariates of the data, we believe it is reasonable to consider all of them relevant, at least at some degree. We thus consider as non-relevant all the artificially added ones. In almost all the bootstrapped subsamples, the reference model improves both in terms of sensitivity and false discovery rate. When $n=50$, we observe a worsening in terms of false discovery rate, yet in a lower amount compared to the gain in sensitivity.  We observe again that the benefits are more evident as the selection is more challenging (i.e. less number of observations). Figure \ref{fig:bodyfat_stability} shows the stability results, still using the measure provided by \cite{paper:stability}. The benefits of the reference model are here marginal: small improvements can be observed, but overall not very notable.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_varyingP_sensitivity_vs_fdr.pdf}
  \caption{Sensitivity against false discovery rate after 100 data simulations.\\}
  \label{fig:bodyfat_varyingP_sensitivity_vs_fdr}
\end{figure}

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_varyingP_stability.pdf}
  \caption{Stability estimates with 0.95 confidence intervals after 100 data simulations.\\}
  \label{fig:bodyfat_varyingP_stability}
\end{figure}

As an additional experiment, we run the selection bootstrapping from the whole dataset, but varying the overall number of covariates from $p=100$ up to $p=5000$. Figures \ref{fig:bodyfat_varyingP_sensitivity_vs_fdr} and \ref{fig:bodyfat_varyingP_stability} respectively show the sensitivity against the false discovery rate and the stability results. As in the previous experiment, we note that the reference model has a larger impact as the complexity of the problem increases: previously as $n$ decreases, now as $p$ increases. Note the different scale of the sensitivity and the false discovery rate axes. We observe an odd behaviour of the selection via credible intervals (ci.90): when $p=100$ and $p=5000$ the results are strongly different from the other methods, both in terms of sensitivity/false discovery rate and stability. 
%Such behaviour can be in part explained by the connection between low stability and high uncertainty in the estimates.

\begin{figure}[tp]
  \centering
  \includegraphics[width=0.98\textwidth]{graphics/bodyfat_step_refvsdata.pdf}
  \caption{Stepwise backward selection using or not the reference model: number of noisy feature included in the model and RMSE after 100 bootstrap samples.\\}
  \label{fig:bodyfat_step_refvsdata}
\end{figure}

Finally, we repeate the selection of Section \ref{projection} implementing the stepwise backward selection by AIC as implemented in the \textit{step} function in R. We have not fixed any variable to be always included in the model and the overall number of covariates (original plus noisy) is 100. We compare results using or not the reference model on top of the procedure; here we have used again the reference model given by the first five supervised principal components. Figure \ref{fig:bodyfat_step_refvsdata} shows the number of noisy features included in the final model and the out-of-sample root mean square error (RMSE). Results are after 100 bootstrap simulations and the predictive performance is tested on the observations excluded at each bootstrap sample. We observe that the reference model reduces the number of noisy features included in the final model. This leads to less overfit to the data and, thus, improved out-of-sample predictive performance in terms of RMSE. Also in this case, we see that there is not a notable difference in terms of the stability of the two approaches, which in this case is qualitatively assessed through the variability of the histogram. We can not use the stability measure provided by \cite{paper:stability}, since it does not take in account possibly swaps in the set of selected features due to high correlation between the covariates, which in this case can occur. Our reference model approach applied to the stepwise backward selection achieves outstanding improvements considering its simplicity, yet it does not reach the goodness of more thoughtful implementations, as projpred (see results of Section \ref{projection}).

We would like the reader to note that in this example we have still used the reference model defined as a linear regression over some supervised principal components, because of its fairly good predictive performance and speed to fit. We do not argue that this is always a good choice, more sophisticated and well-thought models can lead to even better results. Since in our case the sake of the analysis was only explanatory in terms of the comparison we have been carrying out through the paper and needed to average results over many (100) simulations, we preferred to stick to such model.
